Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-01 paper/paper.tex
paper updated

\paragraph{Tasks}
For the optimization to work properly, the problems presented to the networks 
have (for the most part) to solvable by FORCE learning. While it was shown \citep{}
that large recurrent neural networks are capable of learning very complex functions
using the FORCE algorithm, the optimization requires a large number of learnings.
Therefore, the networks have to be restricted to being quite small ($\approx 100$ neurons)
and as such are less powerful.

@@

\paragraph{Success}
In order to optimize the function reconstruction of a force network, a measure $f(g, g^\prime)$ for
the concordance of target $g$ and network output $g^\prime$ is necessary. Simply using the difference
$f_d(g, g^\prime) = \left\| g-g^\prime \right\|_2$ has the drawback that small phase differences could 
produce huge differences in quality, even though $g^\prime$ has the exact same shape as $g$.

A measure that is timeshift independent and maximized for functions of identical shape is the 
maximum of the cross correlation 
\begin{align}
f_c(g, g^\prime) = \max_t \left<g, g^\prime(\cdot - t)\right> / \sqrt{\left< g, g\right> \left<g^\prime, g^\prime \right>}.
\end{align}
Algorithmically, the signals are split into overlapping chunks which are correlated separately. 
This saves computational power and prevents minute differences in frequency to accumulate into 
a huge phase shift, i.e. the phase only has to remain relatively
constant over the timescale of a single chunk (i.e. about 10 seconds of simulated time).

>>>>

\paragraph{Tasks and Challenges}
For the learning to work properly, the problems presented to the
networks have (for the most part) to be solvable by FORCE. While
it was shown \citep{FORCE} that large recurrent neural networks are capable of
learning very complex functions, the optimization requires a large number
of learnings. Therefore, the networks have to be restricted to being quite
small ($\approx 100$ neurons) and are consequently less powerful.

@@

Since we expect/hope that the optimized network extends this range of possible frequencies,
we choose the frequencies for the optimiztion tasks from the slighly larger interval 
$[0.6e-2, 4]$ such that their logarithms are uniformly spaced. This allows for good resolution 
for both high and low frequencies.

\paragraph{Success}
In order to optimize the function reconstruction of a force network,
a measure $f(r', r)$ for the concordance of the target function
$r'(t)$ and the network readout $r(t)$ is necessary. Simply using the
difference $f\ix{d}(r, r') = \left\|r-r'\right\|_2$ has the
drawback that small phase differences could produce huge differences in
quality, even though $r'$ has the exact same shape as $r$.

A measure that is timeshift independent and maximized for functions of identical shape is the 
maximum of the cross correlation 
\begin{align}
    f\ix{c}(r, r') = \max_t \frac{\left<r, r'(\cdot - t)\right>}{\sqrt{\left< r, r\right> \left<r', r' \right>}}~.
\end{align}
Algorithmically, the signals are split into overlapping chunks which are correlated separately. 
This saves computational power and prevents minute differences in frequency to accumulate into 
a huge phase shift, i.e. the phase only has to remain relatively
constant over the timescale of a single chunk (about 10 seconds of simulated time).
